---
title: "02A - Analysis"
author: "Mine Cetinkaya-Rundel"
date: "1/23/2018"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo=FALSE)
```

## Load packages

```{r load-packages, message=FALSE}
library(tidyverse)
```

## The data

The data come from [Kaggle.com](https://www.kaggle.com/srcole/burritos-in-san-diego), 

```{r load-data, message=FALSE}
burritos <- read_csv("../data/burritos_01022018.csv")
```

Mexican cuisine is often the best food option is southern California. And the 
burrito is the hallmark of delicious taco shop food: tasty, cheap, and filling. 
Appropriately, an effort was launched to critique burritos across the county 
and make this data open to the lay burrito consumer. At this time, the data set 
contains ratings from over `r nrow(burritos)` burritos fromd `r burritos %>% count(Location) %>% nrow()` restaurants.

There are 10 core dimensions of the San Diego burrito. * Volume * Tortilla 
quality *Temperature * Meat quality * Non-meat filling quality * Meat-to-filling 
ratio * Uniformity * Salsa quality * Flavor synergy * Wrap integrity

All of these measures (except for Volume) are rated on a scale from 0 to 5, 0 
being terrible, and 5 being optimal. Other information available for each 
burrito includes an overall rating, cost, Yelp rating of the restaurant, and more.

```{r glimpse-data}
glimpse(burritos)
```

## Exploratory data analysis

```{r fig.height = 4, fig.width = 8, fig.cap = "Five most common reviewers"}
burritos %>%
  mutate(Reviewer = fct_lump(Reviewer, n = 5)) %>%
  ggplot(mapping = aes(x = Reviewer)) +
    geom_bar()
```

```{r fig.height = 4, fig.width = 8, fig.cap = "Relationship between Google and Yelp review scores"}
ggplot(data = burritos, mapping = aes(x = Cost, y = overall)) +
  geom_point()
```

