---
title: "San Diego Burritos"
author: "Mine Çetinkaya-Rundel"
date: "2018-01-23"
output: 
  html_document: 
    highlight: pygments
    theme: cosmo
---

## Load packages

```{r load-packages}
library(tidyverse)
```

## The data

The data come from [Kaggle.com](https://www.kaggle.com/srcole/burritos-in-san-diego):

>Mexican cuisine is often the best food option is southern California. And the 
>burrito is the hallmark of delicious taco shop food: tasty, cheap, and filling. 
>Appropriately, an effort was launched to critique burritos across the county 
>and make this data open to the lay burrito consumer. 

```{r load-data}
burritos <- read_csv("../data/burritos_01022018.csv")
```

At this time, the data set 
contains ratings from over `r nrow(burritos)` burritos fromd `r burritos %>% count(Location) %>% nrow()` restaurants.

There are 10 core dimensions of the San Diego burrito. * Volume * Tortilla 
quality *Temperature * Meat quality * Non-meat filling quality * Meat-to-filling 
ratio * Uniformity * Salsa quality * Flavor synergy * Wrap integrity

All of these measures (except for Volume) are rated on a scale from 0 to 5, 0 
being terrible, and 5 being optimal. Other information available for each 
burrito includes an overall rating, cost, Yelp rating of the restaurant, and more.

```{r}
glimpse(burritos)
```

## Exploratory data analysis

First let's take a look at who the reviewers are.

```{r}
burritos_rev_count <- burritos %>%
  mutate(Reviewer = fct_lump(Reviewer, n = 5)) %>%
  count(Reviewer) %>%
  mutate(Reviewer = fct_reorder(Reviewer, n, .desc = TRUE)) %>%
  arrange(desc(n))
burritos_rev_count
ggplot(data = burritos_rev_count, mapping = aes(x = Reviewer, y = n)) +
    geom_bar(stat = "identity") +
    labs(title = "Distribution of reviewers", x = "", y = "")
```

Seems like `r burritos_rev_count$Reviewer[1]`  has been eating a lot of burritos!

Next we visualize the relationship between the cost and overall rating of the burritos. The relationship appears to be positive, though the one extremely expensive burrito makes it difficult to assess the strength of the relationship.

```{r}
ggplot(data = burritos, mapping = aes(x = Cost, y = overall)) +
  geom_point() +
  labs(title = "Overall rating vs. cost", y = "Overall rating")
```

